Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-13 ms.tex
cleaned up4

\item Radiative cooling has a more pronounced influence on the flow structure.  Cooling instabilities are likely to develop when the radiative cooling rate exceeds the gas heating rate near the stagnation radius.  This condition is approximately equivalent to the criterion $t_{\rm cool} \gg t_{\rm ff}$ criterion advocated by \citet{McCourt+12} and \citet{Li&Bryan14a}.

>>>>

\item Radiative cooling has a more pronounced influence on the flow structure.  Cooling instabilities are likely to develop when the radiative cooling rate exceeds the gas heating rate near the stagnation radius.  This condition is approximately equivalent to the $t_{\rm cool} \gg t_{\rm ff}$ criterion advocated by \citet{McCourt+12} and \citet{Li&Bryan14a}.
